A generic and fast C++ optimization framework

### 2017-10-18 paper.tex
Add two more features.

% Just to get a feeling of the look; Also, we could also just use \OK instead of \CURCLE or \LEFTcircle
\begin{table}
\centering
    \begin{tabular}{@{} cl*{4}c @{}}
        & & \multicolumn{4}{c}{} \\[2ex]
        & & \rot{has framework}
          & \rot{\shortstack[l]{problem-independent\\constraints}}
          & \rot{supports x}
          & \rot{supports x} \\
        \cmidrule{2-6}
        & mlpack             & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE  \\
        & vowpal wabbit      &  - & - & -  & -  \\
        & TensorFlow         &  - & -  & -  & -  \\
        & scikit-learn       &  - & -  & -  & - \\
        & scipy              &  - & \LEFTcircle  & \LEFTcircle  & \LEFTcircle \\
        \cmidrule[1pt]{2-6}
    \end{tabular}
    \begin{tablenotes}\footnotesize
\item[*] Library feature comparison: \CIRCLE=\text{provides feature}, \LEFTcircle=\text{partially provides feature}, -=\text{does not provide feature}
\end{tablenotes}
\end{table}

@@

mlpack is a C++ machine learning library with an emphasis on speed, flexibility,
and ease of use \cite{mlpack2013}; it has been continuously developed since
2007.  mlpack uses the Armadillo library \cite{sanderson2016armadillo} for
linear algebra and matrix primitives.  Both mlpack and Armadillo exploit C++
language features such as policy-based design and template metaprogramming to
provide compile-time optimizations that result in fast code \cite{pasc2017},
while retaining a simple and easy-to-use interface \cite{icopust2017}.

@@

\begin{itemize}
  \item {\tt Evaluate()}
  \item {\tt Gradient()}
  \item {\tt PartialGradient()} 
  \item ...
  \item constraints?
  \item discrete variable support?
  \item batch support
\end{itemize}

>>>>

% Just to get a feeling of the look; Also, we could also just use \OK instead of \CURCLE or \LEFTcircle
\begin{table}
\centering
    \begin{tabular}{@{} cl*{6}c @{}}
        & & \multicolumn{6}{c}{} \\[2ex]
        & & \rot{has framework}
          & \rot{\shortstack[l]{problem-independent\\constraints}}
          & \rot{batches}
          & \rot{reusability}
          & \rot{x}
          & \rot{y} \\
        \cmidrule{2-8}
        & mlpack             & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE  \\
        & vowpal wabbit      & - & - & \LEFTcircle  & \CIRCLE & - & - \\
        & TensorFlow         & - & -  & \CIRCLE  & \LEFTcircle & - & -  \\
        & scikit-learn       & - & -  & \CIRCLE  & \LEFTcircle & - & - \\
        & scipy              & - & \LEFTcircle  & -  & \LEFTcircle & - & - \\
        \cmidrule[1pt]{2-8}
    \end{tabular}
    \begin{tablenotes}\footnotesize
\item[*] Library feature comparison: \CIRCLE=\text{provides feature}, \LEFTcircle=\text{partially provides feature}, -=\text{does not provide feature}
\end{tablenotes}
\end{table}

@@

mlpack is a C++ machine learning library with an emphasis on speed, flexibility,
and ease of use \cite{mlpack2013}; it has been continuously developed since
2007.  mlpack uses the Armadillo library \cite{pasc2017} for
linear algebra and matrix primitives.  Both mlpack and Armadillo exploit C++
language features such as policy-based design and template metaprogramming to
provide compile-time optimizations that result in fast code \cite{pasc2017},
while retaining a simple and easy-to-use interface \cite{icopust2017}.

@@

\begin{itemize}
  \item {\tt Evaluate()} Evaluate a function.
  \item {\tt Gradient()}: Evaluate the gradient of a function.

  \item {\tt PartialGradient()} Evaluate the partial (sparse) gradient of a
      function.

  \item ...
  \item constraints?
  \item discrete variable support?
  \item batch support
\end{itemize}
